Learning by Teaching a Robot: the Case of Handwriting

### 2015-07-08 main.tex
number of demonstrations
Changed figure for examples of bad letters

By changing the eigenvalues associated to these eigenvectors and regenerating
letters with the reverse procedure, it becomes then easy to generate new
letters, with distortions that are actually plausible handwriting errors: they
are actually \emph{exaggerations} of variance of writing styles that naturally
exist amongst adult writers.  Figure~\ref{fig:sampleLetters} shows examples of
deformed ``e'' and ``g'' generated with such a technique.

\begin{figure}[thpb]
\centering
\subfigure{\raisebox{-0.5\height}{\includegraphics[width=0.08\columnwidth]{e1.png}}}
\subfigure{\raisebox{-0.5\height}{\includegraphics[width=0.08\columnwidth]{e4.png}}}
\subfigure{\raisebox{-0.5\height}{\includegraphics[width=0.08\columnwidth]{e3.png}}}
\subfigure{\raisebox{-0.5\height}{\includegraphics[width=0.08\columnwidth]{e5.png}}}~~~~~
\subfigure{\raisebox{-0.5\height}{\includegraphics[width=0.06\columnwidth]{g1.png}}}
\subfigure{\raisebox{-0.5\height}{\includegraphics[width=0.06\columnwidth]{g3.png}}}
\subfigure{\raisebox{-0.5\height}{\includegraphics[width=0.06\columnwidth]{g4.png}}}
\subfigure{\raisebox{-0.5\height}{\includegraphics[width=0.06\columnwidth]{g5.png}}}
\caption{\small \label{fig:sampleLetters}Sample letters generated from the PCA shape
model on ``e'' (left) and ``g'' paths (right), generated randomly from
parameters with $3\times$ the standard deviation observed in the dataset.}

>>>>

By changing the eigenvalues associated to these eigenvectors and regenerating
letters with the reverse procedure, it becomes then easy to generate new
letters, with distortions that are actually plausible handwriting errors: they
are actually \emph{exaggerations} of variance of writing styles that naturally
exist amongst adult writers.  Figure~\ref{fig:sampleLetters} shows examples of
deformed ``g'' generated with such a technique.

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{cowriter-g}
    \caption{\small \label{fig:sampleLetters} \textbf{Generating bad letters}:
        effect of varying the first five eigenvalues (rows) of the shape model
        of ``g'' by different factors (columns). The percentage of the total
        variance in the dataset explained by each eigenvalue is shown      on
        the appropriate row.}
